Author contributions are listed below. \\
Husni Almoubayyed: wrote an mcmc jupyter notebook example, reviewed code/contributed to issues. \\
David Alonso: Co-led project; developed structure for angular power spectra; implemented autotools; integrated into LSS pipeline; contributed to: background, power spectrum, mass function, documentation and benchmarks; reviewed code \\
M.~R.~Becker: Core code and algorithmss \\
Jonathan Blazek: Planning capabilities and structure; documentation and testing. \\
Philip Bull: Implemented the Python wrapper and wrote documentation for it; general bug fixes, maintenance, and code review; enhanced the installer and error handling system. \\
Jean-\'Eric Campagne: Angpow builder and contributed to the interface with CCL. \\
N. Elisa Chisari: Co-led project, coordinated hack projects \& communication, contributed to: correlation function \& power spectrum implementation, documentation, and comparisons with benchmarks. \\
Alex Drlica-Wagner: Helped with document preparation. \\
Zilong Du: Implemented the 3d correlation function, redshift-space correlation functions, and corresponding benchmarks. \\
Tim Eifler: Reviewed/tested code. \\
John Ellison: Implemented the 3d correlation function, redshift-space correlation functions, and corresponding benchmarks; wrote documentation. \\
Cristhian Garcia Quintero: Produced benchmarks for correlation functions in modified gravity. \\
Ren\'ee Hlozek: Contributed initial code for error handling structures, reviewed other code edits. \\
Mustapha Ishak: Contributed to planning of code capabilities and structure; reviewed code; identified and fixed bugs. \\
Shahab Joudaki: Created physical density function and documentation. \\
Matthew Kirby: Performed comparison of physical constants. \\
David Kirkby: Writing, testing and reviewing code. Asking questions. \\
Elisabeth Krause: Initiated and co-led project; developed CLASS interface and error handling; contributed to other code; reviewed pull requests. \\
Francois Lanusse: Worked on install procedure \\
C. Danielle Leonard: Wrote and tested code for LSST specifications, user-defined photo-z interface, and support of massive neutrinos; reviewed other code; wrote text for this note. \\
Christiane S. Lorenz: Contributed to accurate high-redshift cosmological background quantities and benchmarked background splines. \\
Phil Marshall: Helped with document preparation. \\
Thomas McClintock: Wrote Python documentation. \\
Sean McLaughlin: Wrote doxygen documentation and fixed bugs/added functionality to distances. \\
Alexander Mead: Wrote halo model code \\
J\'er\'emy Neveu: Contributed to Angpow and built the interface with CCL. \\
St\'ephane Plaszczynski: Contributed to Angpow and contributed to the interface with CCL. \\
Javier Sanchez: Modified setup.py to allow pip installation and uninstall. \\
Sukhdeep Singh: Contributed to the correlation functions code. \\
An\v{z}e Slosar: Wrote and reviewed code. \\
Tilman Tr\"oster: Wrote code for user-changable precision parameters, added distance and growth factor tests, found and fixed bugs. \\
Antonio Villarreal: Contributed to initial benchmarking, halo mass function code, and general code and issues review. \\
Michal Vrastil: Wrote documentation and example code, reviewed code. \\
Kuan Wang: Wrote halo profiles code. \\
Joe Zuntz: Wrote initial infrastructure, C testing setup, and reviewed code. \\
