Author contributions are listed below. \\
Nora Elisa Chisari: Co-led project, coordinated hack projects \& communication, contributed to: correlation function \& power spectrum implementation, documentation, and comparisons with benchmarks. \\
David Alonso: Co-led project; developed structure for angular power spectra; implemented autotools; integrated into LSS pipeline; contributed to: background, power spectrum, mass function, documentation and benchmarks; reviewed code \\
Elisabeth Krause: Initiated and co-led project; developed CLASS interface and error handling; contributed to other code; reviewed pull requests. \\
C. Danielle Leonard: Wrote and tested code for LSST specifications, user-defined photo-z interface, and support of neutrinos; reviewed other code; wrote text for this note. \\
Philip Bull: Implemented and documented the Python wrapper; extensive infrastructure work, including maintenance of the build system and unit tests, bug fixes, and code review; enhanced the error handling system; performed power spectrum comparison across parameter space; various architecture/design contributions. \\
J\'er\'emy Neveu: Contributed to Angpow, built the interface with CCL and the comparisons with benchmarks. \\
Antonio Villarreal: Contributed to initial benchmarking, halo mass function code, and general code and issues review. \\
Sukhdeep Singh: Contributed to the correlation functions code and weak lensing benchmarks. \\
Thomas McClintock: Wrote Python and doxygen documentation. \\
John Ellison: Implemented the 3d correlation function; documentation of 3d correlation function. \\
Zilong Du: Implemented the 3d correlation function. \\
Joe Zuntz: Wrote initial infrastructure, C testing setup, and reviewed code. \\
Alexander Mead: Wrote halo-model code and documentation \\
Shahab Joudaki: Performed benchmarking of angular power spectra and correlation functions for galaxy clustering, galaxy-galaxy lensing, and cosmic shear (including intrinsic alignments); reviewed all CCL benchmarks; contributed to implementation of background functions and documentation. \\
Christiane S. Lorenz: Contributed to accurate high-redshift cosmological background quantities and benchmarked background splines. \\
Tilman Tr\"oster: Wrote code for user-changable precision parameters and distance tests, found and fixed bugs. \\
Javier Sanchez: Modified setup.py to allow pip installation and uninstall. \\
Francois Lanusse: Contributed to improving installation options. \\
Mustapha Ishak: Contributed to planning of code capabilities and structure; reviewed code; identified bugs and wrote code to fix them; wrote text for this note. \\
Ren\'ee Hlozek: Contributed initial code for error handling structures, reviewed other code edits. \\
Jonathan Blazek: Planning capabilities and structure; documentation, review, and testing. \\
Jean-Eric Campagne: Angpow main builder. \\
Husni Almoubayyed: Reviewed code/contributed to example notebooks and issues. \\
Tim Eifler: Reviewed/tested code. \\
Matthew Kirby: Performed comparison of physical constants. \\
David Kirkby: Writing, testing and reviewing code. Asking questions. \\
St\'ephane Plaszczynski: Contributed to Angpow. \\
An\v{z}e Slosar: Wrote and reviewed code. \\
Michal Vrastil: Wrote documentation and example code, reviewed code. \\
Erika L. Wagoner: Set up logarithmic binning in wave number. \\
